Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-01-26 Paper.tex
\begin{tabu}{X[l]X[c]X} \savetabu{col3}
Move \hypertarget{bigvee}{} to preceding line
Remove parentheses

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabularx}{\textwidth}{lcX}
\toprule
Symbol & Latex Command & Description \\
\midrule
\hypertarget{bigvee}{}
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements (\cite{Davey2002_zbMATH01748069}).\\
\bottomrule
\end{tabularx}

>>>>

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabu}{X[l]X[c]X} \savetabu{col3}
\toprule
Symbol & Latex Command & Description \hypertarget{bigvee}{}\\
\midrule
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements \cite{Davey2002_zbMATH01748069}.\\
\bottomrule
\end{tabu}
